What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-08-26 paper/main.tex
added funding

\author{\IEEEauthorblockN{Runming Li\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\textit{Carnegie Mellon University}\\
Pittsburgh, USA \\
runmingl@andrew.cmu.edu}
\and
\IEEEauthorblockN{Keerthana Gurushankar\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\textit{Carnegie Mellon University}\\
Pittsburgh, USA \\
kgurusha@andrew.cmu.edu}
\and
\IEEEauthorblockN{Marijn~J.H.~Heule}
\IEEEauthorblockA{\textit{Carnegie Mellon University}\\
Pittsburgh, USA \\
marijn@cmu.edu}
\and
\IEEEauthorblockN{Kristin~Y.~Rozier}
\IEEEauthorblockA{\textit{Iowa State University} \\
Ames, USA \\
ekyrozier@iastate.edu}
}

@@

>>>>

\author{\IEEEauthorblockN{Runming Li\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\textit{Carnegie Mellon University}\\
Pittsburgh, USA \\
runmingl@andrew.cmu.edu}
\and
\IEEEauthorblockN{Keerthana Gurushankar\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\textit{Carnegie Mellon University}\\
Pittsburgh, USA \\
kgurusha@andrew.cmu.edu}
\and
\IEEEauthorblockN{Marijn~J.H.~Heule}
\IEEEauthorblockA{\textit{Carnegie Mellon University}\\
Pittsburgh, USA \\
marijn@cmu.edu}
\and
\IEEEauthorblockN{Kristin~Y.~Rozier}
\IEEEauthorblockA{\textit{Iowa State University} \\
Ames, USA \\
kyrozier@iastate.edu}
}

@@

\section*{Acknowledgements}

This work was partially supported by the National Science Foundation (NSF) under grants CCF-2015445, CAREER-1664356, and CCRI-2016592.
